### 2018-11-07 inst/table_tennis_serve.Rmd
rewording

On the null, Wilks's theorem says that $\Lambda\sim\chi^2_1$, where
$\Lambda=2\log(L_1/L_2)$, so the
p-value is

@@

The difference in support, ```delta_support```, is about 2.62 which
exceeds Edwards's two-units-of-support criterion.  The likelihood
ratio LR is about 13.7, and Wilks's theorem gives us that
$\Lambda=2\log(LR)$ is distributed as chi-squared with one degree of
freedom; the tail area, pval, is about 0.022 which gives us a
significant result.

>>>>

The difference in support, ```delta_support```, is about 2.62 which
exceeds Edwards's two-units-of-support criterion.  We can reject the
null.  Alternatively, Wilks's theorem gives us that
$\Lambda=2\log(LR)$ is distributed as chi-squared with one degree of
freedom:

@@

Thus the tail area, pval, is about 0.022 which gives us a significant
result.
